\name: A hierarchical Bayesian model for Supernova Cosmology

### 2018-09-18 papers/methods/paper.tex
Updating paper

\begin{table}
	\centering
	\caption{Investigating the combined 100 fits to {\gten} and {\celeven} simulations, fitting with both statistics only and also when including systematics. The quoted value for $w$ represents the average mean of the fits, with the uncertainty being the average standard deviation of the fits. In brackets, the simulation scatter (the standard deviation of the mean of 100 fits) is shown, and the bias significance represents our confidence that the deviation in the mean $w$ away from $-1$ is not due to statistical fluctuation. With systematics enabled, both the {\gten} and {\celeven} models show evidence of bias, scattering to either side of the simulated value of $w=-1$. However, their deviation from the truth value represents a shift of approximately $0.3\sigma$ when taking into account the uncertainty on fits to $w$. {\green The bias is sub-dominant to both the size of the uncertainty for each fit, and the scatter induced by statistical variance in the simulations. We also note that the simulations do not vary cosmological parameters nor population. As our model does include uncertainty on those values, the simulation scatter is expected to be less than the model uncertainty, and represents a minimum bound on permissible uncertainty values.}}
	\label{tab:bulk_summary}
	\begin{tabular}{l|cc}
		\hline
		Model & $w$ (scatter) & Bias \\
		\hline
		{\gten} Stat + Syst  &  $-1.03\pm 0.10\ (0.08)$ & $0.3\sigma$  \\
		{\celeven} Stat + Syst  &  $-0.97\pm 0.09\ (0.06)$ & $0.3\sigma$  \\
		{\gten}  Stat         &  $-1.01\pm 0.08\ (0.08)$ & $0.1\sigma$   \\
		{\celeven} Stat         &  $-0.96\pm 0.07\ (0.05)$ & $0.6\sigma$   \\
		\hline
	\end{tabular}
\end{table}

@@

>>>>

\begin{table}
	\centering
	\caption{Investigating the combined 100 fits to {\gten} and {\celeven} simulations, fitting with both statistics only and also when including systematics. The quoted value for $w$ represents the average mean of the fits, with the uncertainty being the average standard deviation of the fits. In brackets, the simulation scatter (the standard deviation of the mean of 100 fits) is shown, and the bias significance represents our confidence that the deviation in the mean $w$ away from $-1$ is not due to statistical fluctuation. With systematics enabled, both the {\gten} and {\celeven} models show evidence of bias, scattering to either side of the simulated value of $w=-1$. However, their deviation from the truth value represents a shift of approximately $0.3\sigma$ when taking into account the uncertainty on fits to $w$. {\green The bias is sub-dominant to both the size of the uncertainty for each fit, and the scatter induced by statistical variance in the simulations. We also note that the simulations do not vary cosmological parameters nor population. As our model does include uncertainty on those values, the simulation scatter is expected to be less than the model uncertainty, and represents a minimum bound on permissible uncertainty values.}}
	\label{tab:bulk_summary}
	\begin{tabular}{l|cc}
		\hline
		Model & $w$ (scatter) & Bias \\
		\hline
		{\gten} Stat + Syst  &  $-1.00\pm 0.10\ (0.08)$ & $0.0\sigma$  \\
		{\celeven} Stat + Syst  &  $-0.95\pm 0.10\ (0.06)$ & $0.5\sigma$  \\
		{\gten}  Stat         &  $-1.00\pm 0.08\ (0.08)$ & $0.0\sigma$   \\
		{\celeven} Stat         &  $-0.95\pm 0.08\ (0.05)$ & $0.6\sigma$   \\
		\hline
	\end{tabular}
\end{table}

@@

BHM Mean for G10: -0.998, BBC mean -1.042, average diff -0.044, difference scatter 0.057

BHM Mean for C11: -0.945, BBC mean -0.978, average diff -0.033, difference scatter 0.062

{\red For systematics paper, also find 60\% reduction in uncert using planck priors}

\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{bulk_comparison.pdf}
	\end{center}
	\caption{Whoa.}
	\label{fig:bulk_comparison}
\end{figure}
